% !TEX program = lualatex
\documentclass{article}

\title{Marriage Guidelines}
\author{Rev. Gregory R. Barnes}

%\usepackage{fancyhdr}
%\pagestyle{fancy}

\usepackage{fontspec}
\setmainfont{Minion 3}

\usepackage{framed}

\usepackage{ragged2e}

\begin{document}

\maketitle

%\tableofcontents

\newcommand{\inspection}[2]{
    \begin{framed}
        \begin{Center}
            \textit{
                The #1 shall be submitted #2 before the wedding to be inspected
                by the marriage instructor.
            }
        \end{Center}
    \end{framed}
}

\section{General}

\subsection{Social Media}

If posts\footnote{Includes text, images, audio and videos.} deemed indecent by
the clergy are posted on any public platform, whether taken down or made
private, and regardless of a public or private retraction or apology having or
not having been made, the wedding shall take place without wedding dress,
Nuptial blessing, Mass or choir.

\subsection{Fornication}

If one not having been previously married has become publicly known to be
pregnant before the marriage the wedding shall take place without wedding dress,
Nuptial blessing, Mass or choir.


\section{Dresses}

\subsection{Toleration}

Under no circumstances will immodest dress be tolerated. If the bride or her
bridesmaids are seen on the church property wearing gowns not in conformity
with these guidelines, the wedding is subject to immediate cancellation.

\subsection{Forbidden Garments}

\begin{enumerate}
    \item Strapless dresses.
    \item ``Noodle'' or ``spaghetti'' strap dresses.
    \item Sleeveless dresses.
    \item Wrap dresses.
    \item Dresses with slits.
    \item Open toed shoes.
    \item Shoes with heels higher than 1 inch.
\end{enumerate}

\subsection{Shawls, etc.}

An improper gown shall not be covered with a shawl, scarf, wrap, or any other
removeable garment. All material used to replace material that is lacking in
the garment is to be premanently fixed to the garment. To refuse to affix such
replacement material to the garment will result in cancellation of the wedding.

\subsection{Lace $=$ Nothing}

When altering gowns, \textit{opaque} fabric is to be used. Sheer fabric or lace
will not be tolerated.

If you wish to use lace, the lace must have an opaque backer. No exceptions will
be made.

\subsection{Neckline}

The neckline shall be no more than two fingers' breadth lower
than the collarbone. No exceptions will be made.

\subsection{Back}

The back of the bodice shall not be open. The neckline on the back shall not be
any lower than the neckline in the front.

\subsection{Straps}

Strapless dresses will not be tolerated, under any circumstances.

\subsection{Sleeves}

\begin{enumerate} 
    \item The dress shall not be sleeveless. 
    \item The dress shallhave long sleeves.\footnote{Short sleeves that 
            completely cover the biceps are permitted.} 
\end{enumerate}

\subsection{Bodice}
\begin{enumerate}
    \item The bodice shall not be tight or revealing in any way.
    \item The bodice shall be made of an opaque material and shall not be
        transparent or semi-transparent in any way.
\end{enumerate}

\subsection{Skirt}

\begin{enumerate}
    \item The skirt of the dress shall not be tight in any way.
    \item The skirt of the gown shall not be revealing in any way.
    \item The skirt of the dress shall not have slits.
    \item The entire hem of the skirt shall reach at least the ankles.
\end{enumerate}

\subsection{Length}

The dress shall be ankle length.


\section{Bride}

\subsection{Dress}

\begin{enumerate}
    \item The color of the dress may be white.\footnote{As is the custom in the
        United States.}
    \item Brides who are marrying a second time shall wear a dark blue dress,
        which shall conform to all the above restrictions and requirements. Such
        brides shall not wear a veil before the face.\footnote{Such a veil is a
        sign of virginity.}
\end{enumerate}

\inspection{dress}{one month}

\subsection{Veil}

The veil shall cover the head. If the veil is not deemed by one of the priests
to sufficiently cover the head, the veil shall be adjusted until the head is
sufficiently covered. Failure to comply will result in immediate cancellation of
the wedding.

\inspection{veil}{one month}

\section{Groom}


\section{Bridal Party}

\subsection{Dress}

All of the gowns worn by the bridesmaids shall be ankle-length.


\section{In the Church}

\subsection{Dress Code}

All guests shall conform to the chapel's dress code.

\begin{framed} 

    \textbf{For men:} Jacket and tie. No earrings. No shorts. 

    \textbf{For ladies:} A dress or skirt is required; no pants or shorts. The
    skirt must at least cover the knee, and should not be tight or otherwise
    revealing in any way. Immodest slits are forbidden. \textbf{Clothing should
    be loose and not form-fitting}. A head covering is also required.
    See-through blouses are forbidden, as well as clothing which is low-cut
    either in front or in back.
    
    \textbf{For everyone:} No \textbf{tennis shoes, sandals, clogs, thongs,
    denim}. No piercings. Clothing with writing on it (e.g., sweatshirts or
    jackets) is also forbidden. The standards of Catholic modesty must be
    observed. \textbf{Anyone in tight, provocative, or otherwise revealing
    attire will not be permitted to enter the church.} 

\end{framed}

Those who enter the chapel with clothing not in conformity with the dress code
will be presented with a gown with which to cover themselves (e.g. a graduation
gown). Those who do not choose to wear the garment presented to them will be
asked to leave the property. No exceptions will be made.

\subsection{Ceremony}

\begin{enumerate}
    \item Bride and groom do not hold hands until told to do so by the
        priest.
    \item There is no kissing:
        \begin{enumerate}
            \item The father of the bride does not kiss the bride before passing
                her to the groom.
            \item The bride and groom never kiss.
        \end{enumerate}
    \item Groomsmen and bridesmaids do not lock arms or hold hands at any time.
\end{enumerate}


\section{Reception}

\begin{enumerate}
    \item There is no removal of the garter. 
    \item There is no clinking of glasses so that the bride and groom may kiss.
\end{enumerate}

\subsection{Music}

All rock music is forbidden. 

\inspection{playlist}{one week}

The following are some but not all of the forbidden singers or groups:

\begin{enumerate}
    \item Elvis Presley
    \item The Beatles
\end{enumerate}

\end{document}
